\section{Anodyne extensions}

For references for this section see \cite[Section I.4]{GoerSimp1999}.

\begin{defi}
    We say that a class $\mathcal{M}$ of morphisms in $\mathcal{C}$ is a \underline{saturated class} if 
    \begin{enumerate}
        \item 
        $\mathcal{M}$ contains all isomorphisms,
        \item 
        $\mathcal{M}$ is closed under compositions,
        \item
        if $i:L \to K$ is in $\mathcal{M}$ then so is the pushout $i'$ given by the pushout diagram 
        \[
        \begin{tikzcd}
            L
            \arrow[d,"i"]
            \ar[r,"\sigma"]
            &
            L'
            \ar[d,"i'"]
            \\
            K
            \ar[r]
            &
            K'   
        \end{tikzcd}
        \]
        \item
        $\mathcal{M}$ is closed under coproducts and
        \item 
        for any sequence of objects and morphism 
        \[
        L^{(0)} \to L^{(1)} \to L^{(2)}\to \dotsc
        \]
        in $\mathcal{M}$, the morphism $L^{(0)} \to L^{(\infty)}=\colim L^{(n)}$ is in $\mathcal{M}$.
    \end{enumerate}
    We say that $\mathcal{M}$ is a saturated class of monomorphisms if all $i \in \mathcal{M}$ are monomorphisms.
\end{defi}

\begin{defi}
    The \underline{saturation} of a class of monomorphisms is the intersection of all such containing it. We write $\overline{\mathcal{M}}$ for its saturation.
\end{defi}

\begin{defi}
    The class of anodyne extensions is $\overline{\{ \Lambda_k^n \xrightarrow{i_k^n} \Delta^n \mid 1 \leq n ,0 \leq k \leq n \}}=\An$.
\end{defi}

\begin{rmk}
    The term anodyne extensions translates to something like harmless extensions.
\end{rmk}

\begin{prop}
    The class $\An^{\lift{}}$ is equal to the Kan fibrations.
\end{prop}

\begin{proof}
    $(\subseteq)$ Let $p \in \An^{\lift{}}$, then for all $n\geq 0$ there exists $0 \leq k \leq  n$ such that $i_{n,k} \lift{} p: p \in \KanFib$

    $(\supseteq)$ Consider $\prescript{\lift{}}{}{\KanFib}$, this is a saturated class. 
    By unitality of $\An \subseteq \prescript{\lift{}}{}{\KanFib}$ it holds that for all $i \in  \An$ and all $p \in \KanFib$ $i\lift{}p $ which means that for all $p \in \KanFib$ we have that $p \in \An^{\lift{}}$
\end{proof}

\subsection{Exercises}

\begin{Exercise}
    
We define the class of trivial Kan fibrations to be $ r ( \{ \partial \Delta^n \to \Delta^n \mid n \in \mathbb{ N }_0 \} ) $ in $ \SetD $.
Furthermore, let $ \mathcal{ F } $ be the smallest saturated class containing all boundary inclusions $ \{ \partial \Delta^n \to \Delta^n \mid n \in \mathbb{ N }_0 \} $.

\begin{enumerate}[label=(\alph*)]
    \item 
    Show that $ r ( \mathcal{ F } ) $ is the class of trivial Kan fibrations.

    \item 
    Show that $ \mathcal{ F } $ contains all monomorphisms. Proceed as follows.

    \begin{itemize}
        \item 
        For a fixed monomorphism $ \iota : X \to Y $ construct a filtration of $ Y $ by $ X \cup \bold{sk_{n-1}} ( Y ) $ starting with $ X = X \cup \bold{sk_{-1}}( Y ) $, similar to the skeletal filtration from Exercise 7.2. 
        Here $ X \cup \bold{sk_n} ( Y ) $ is defined as pushouts of $ \bold{ sk_n } ( Y ) $ and the image of $ \iota $ along their intersection.

        \item 
        Observe that $ \iota $ is the transfinite composition of this filtration.

        \item 
        Show that the morphisms $ X \cup \bold{sk_{n-1]}}( Y ) \to X \cup \bold{ sk_n }( Y ) $ is pushout of morphisms in $ \mathcal{ F } $ for all $ n \in \mathbb{ N }_0 $ by construction a similar pushout diagram as for the skeletal filtration.
    \end{itemize}

    \item 
    Deduce that $\mathcal{ F }$ is the class of monomorphisms.

    \item 
    Conclude that a trivial Kan fibration is a Kan fibration.
    
\end{enumerate}

\end{Exercise}

\begin{Exercise}
    
We have shown in the lecture that the saturated closure of the horn inclusions 
\[
    \mathcal{B}_1 
    \coloneqq 
    \{ \Lambda_k^n \subseteq \Delta^n \mid 0 \leq k \leq n \in \mathbb{ N }_+ \}
\]
agrees with the saturated closure of
\[
    \mathcal{B}_2
    \coloneqq
    \{ ( \Delta^1 \times \partial\Delta^n) \cup ( \{ \epsilon \} \times \Delta^n ) \subseteq ( \Delta^1 \times \Delta^n ) \mid n \in \mathbb{ N }_0 , \\epsilon \in \Delta_0^1 = \{ 0 , 1 \} \}.
\]
We call this class the anodyne extensions $ \bold{ An }$.
Show that $ \bold{ An } $ agrees with the saturated closure of 
\[
    \mathcal{ B }_3 
    \coloneqq
    \{ ( \Delta^1 \times X ) \cup ( \{ \epsilon \} \times Y ) \subseteq ( \Delta^1 \times Y ) \mid  \epsilon \in \Delta_0^1 = \{ 0 , 1 \} , X \to Y \text{ monomorphism } \}.
\]

\end{Exercise}




    